Truthfulness Verification System

### 2011-04-27 proposal/paper.tex
Started writing algorithm 1w

{\em Mar 29 to Apr 12}
See page~[\pageref{Mar29toApr12}] of section~\ref{sec:UseOfWikipedia}
\begin{itemize}
\item Extraction of meaningful entities(noun phrase) in topic unit and dount unit by checking all combination of content words
\item Ranking based on co-occurence of content words in the interesction of bag of words generated from wiki-articles. 
\item Extracting 
\end{itemize}

@@

\subsubsection{Use of Wikipedia}
\label{sec:UseOfWikipedia}
Although structured databases such as Freebase, DBPedia extract the information from Wikipedia and format them into a structured and query-friendly way, it does not contain all the relevant information all the time. For example, consider the following sentence:

\emph{Les Paul invented the electric guitar}

The wikipedia page "http://en.wikipedia.org/wiki/Electric\_guitar" contains the inventor of the electric guitar in one of the sentences in the body. But this information is not available in the Freebase.

We can use a very simple and elegant method to find the relevant information from Wikipedia by using simple web-scrapping and pattern matching using regular expression. The process is described below.

%When we do a regular expression search of the $DU$ "Les Paul" in these two sentences, we do not get any match. Hence we can conclude that the statement is not true.

\subsubsection{Bag of words}
\begin{enumerate}
\item Step I: Detection of wiki articles from $DU$, $AU$, $TU$.
\begin {enumerate}
\item For the $AU$s, we take the words as they appear in the output of T-verifier(mainly because most of them are single word). For $TU$ we use a basic exponential algorithm that takes all possible combinations of the content words.
\item The default configuration of T-verifier generates a total of 5 $AU$s, without any ranking.  For each content word in a $AU$, or a combination of words in case the $AU$ consists of multiple content words, we check if there exists a wikipedia article. There may be three cases:
\begin{enumerate}
\item No article. Continue with next word or word combination. 
\item One article. Go to next step
\item More than one article. The page lands into a "disambiguation" page. We discuss this later. 
\end{enumerate}
\end{enumerate}
\item We remove the html tags from the pages, and convert them into simple bag of words. Repetation of a word if any is retained.
\item We select the following pairwise combination - a wikiarticle detected from $AU$, ($W_{au_{i}}$) and a wikiarticle detected from $TU$ ($W_{tu_{j}}$).
\item We take the common words $c_{ij} = {w_{1}, w_{2}, \ldots}$ matched by regular expressions in these two bags.
\item Since this is a regular expression matching we will have two different values for $c_{ij}$ = common($W_{au_{i}}$, $W_{tu_{j}}$) and $c_{ji}$ = common($W_{tu_{j}}$, $W_{au_{i}}$). This is explained below.
\item In this collection of common words, $c_{ij}$, we search each of the content words of the $TU$, not included in the title of $W_{tu_{j}}$ 
\item We observe the maximum number of matches in all of such interesctions and use the count to rank the $AU$-s generated by T-verifer. 
\end{enumerate}

\subsubsection{Sentence Splitting}

\subsubsection{Les Paul invented the electric guitar}
The alternative units for this sentence are "Les Paul", "rickenbacker", "Gibson", "Leo", and "Lloyd". Now there is inherent ambiguity about the true inventor of the electric guitar. And Wikipedia does not specify rickenbacker as the inventor of electric guitar. Rather it specify Les Paul as the inventor in several places. Our algorithm unambigiously classify Les Paul as inventor of electric guitar in a similar way for the Sleepless in Seattle case described in the previous subsection.

%On reading the articles related above, there is no information that Rickenbacker actually inventing the electric guitar. He was a founding member of the Rickenbacker company that produces electric guitar. Les Paul on the other hand was a pioneer in designing and developing of what a prototype. Moreover, some of the categories attached with the Les Paul page are American musical instrument makers, Guitar makers, Inventors of musical instruments, National Inventors Hall of Fame inductees. In comparison Adolph Rickenbaker page has only one guitar related category - Guitar stubs, meaning the article is stuck in content.
\subsubsection{Luna 2 is the first spacecraft on the moon}
The alternative units for this sentence are "Luna 2", "Apollo", "Land", "Landing", and "Nasa". Our algorithm returns true for both Luna 2 and Apollo and return false for all others. Now, both Luna 2 and Apollo are in reality true considering the facts that Luna 2 was the first unmanned spacecraft and Apollo was the first manned spacecraft. Hence, we can't say one of the Luna 2 or Apollo as false if farther information is not given. So algorithm 2 can produce correct result for this sentence also.

\subsubsection{Sullivan is the fastest swimmer in the world}
The alternative units for this sentence are "Sullivan", "Michael phelps", "ALexander", "Long", and "Ernest". Similar to the previous sentence, the algorithm 2 can not produce good ranking for for this sentence. However, our algorithm 1 produces correct ranking and together they produce overall correct result

@@

\section{Conclusion}
It this paper, we described current system for truthfulness verification of statements found in the web called T-Verifier and described the possible improvements to the current system. We will primarily use authentic information sources such as Wikipedia and Ontologies extracted from Wikipedia such as FreeBase, DBPedia, and YOGA to found the truthfulness of doubtful statements.

>>>>

{\em Mar 29 to Apr 12}
See page~[\pageref{Mar29toApr12}] of section~\ref{sec:UseOfWikipedia}
\begin{itemize}
\item Extraction of meaningful entities(noun phrase) in topic unit and dount unit by checking all combination of content words
\item Ranking based on co-occurence of content words in the interesction of bag of words generated from wiki-articles. 
\item Ranking based on co-occurence of content words in the sentences generated from wiki-articles. 
\end{itemize}

@@

\section{Wikipedia API}

@@

\section{Use of Wikipedia}
\label{sec:UseOfWikipedia}
We have tried two approaches for using the Wikipedia. In both we utilize the content words to identify articles and there upon treat them separately. In the first approach we treat the articles as bag of words and do not consider the sentence structure and in the next approach we retain the logical structure of each sentence and try to infer from word overlaps.
%When we do a regular expression search of the $DU$ "Les Paul" in these two sentences, we do not get any match. Hence we can conclude that the statement is not true.

\subsection{Bag of words}

\begin{algorithm}
\small
\caption{Ranking Algorithm 1}
\label{alg:AssignScore1} 
\begin{algorithmic}
\STATE \textbf{Description}: Given the alternate units generated by the current T-verifier system, rank the units in descending order of truthfulness using Wikipedia
\STATE \textbf{Input}: alter\_units.txt genereated by T-verifier. Each line in this file is a tuple containing the sentence id, the alternate units generated and the topic unit.
\STATE \textbf{Output}: Ranked alter\_units 
\FOR {each sentence $s_{i}$}
	\STATE $tu_{i}$ = topic unit string
	\STATE $s_{i}.tu\_list$ = find\_wikiarticles\_tu($tu_{s_{i}}$)

	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
	\ENDFOR
	\FOR {each alternate unit $s_{i}.au_{j}$ in $s_{i}.au\_list$ }
		\STATE $bow_{s_{i}.au_{j}}$ = find\_wikiarticles\_au($s_{i}.au_{j}$)
	\ENDFOR	
	%\FOR{every wiki\_article $w_{p}$ in $list_wiki_articles_au_{s_{i}}$ }
	%	$bow_w_{p}$ = generate\_bag\_of\_words($w_{p}$)	
	%	\FOR {every wiki\_article $w_{j}$ in $list_wiki_articles_tu_{j}$  }	
	%	\ENDFOR
	%\ENDFOR
\ENDFOR

\begin{enumerate}
\item Step I: Detection of wiki articles from $DU$, $AU$, $TU$.
\begin {enumerate}
\item For the $AU$s, we take the words as they appear in the output of T-verifier(mainly because most of them are single word). For $TU$ we use a basic exponential algorithm that takes all possible combinations of the content words.
\item The default configuration of T-verifier generates a total of 5 $AU$s, without any ranking.  For each content word in a $AU$, or a combination of words in case the $AU$ consists of multiple content words, we check if there exists a wikipedia article. There may be three cases:
\begin{enumerate}
\item No article. Continue with next word or word combination. 
\item One article. Go to next step
\item More than one article. The page lands into a "disambiguation" page. We discuss this later. 
\end{enumerate}
\end{enumerate}
\item We remove the html tags from the pages, and convert them into simple bag of words. Repetation of a word if any is retained.
\item We select the following pairwise combination - a wikiarticle detected from $AU$, ($W_{au_{i}}$) and a wikiarticle detected from $TU$ ($W_{tu_{j}}$).
\item We take the common words $c_{ij} = {w_{1}, w_{2}, \ldots}$ matched by regular expressions in these two bags.
\item Since this is a regular expression matching we will have two different values for $c_{ij}$ = common($W_{au_{i}}$, $W_{tu_{j}}$) and $c_{ji}$ = common($W_{tu_{j}}$, $W_{au_{i}}$). This is explained below.
\item In this collection of common words, $c_{ij}$, we search each of the content words of the $TU$, not included in the title of $W_{tu_{j}}$ 
\item We observe the maximum number of matches in all of such interesctions and use the count to rank the $AU$-s generated by T-verifer. 
\end{enumerate}

\subsection{Sentence Splitting}

\subsubsection{Les Paul invented the electric guitar}
The alternative units for this sentence are "Les Paul", "rickenbacker", "Gibson", "Leo", and "Lloyd". Now there is inherent ambiguity about the true inventor of the electric guitar. On reading the articles related above, there is no information that Rickenbacker actually inventing the electric guitar. He was a founding member of the Rickenbacker company that produces electric guitar. Les Paul on the other hand was a pioneer in designing and developing of what a prototype. Moreover, some of the categories attached with the Les Paul page are American musical instrument makers, Guitar makers, Inventors of musical instruments, National Inventors Hall of Fame inductees. In comparison Adolph Rickenbaker page has only one guitar related category - Guitar stubs, meaning the article is stuck in content.

\subsubsection{Luna 2 is the first spacecraft on the moon}
The alternative units for this sentence are "Luna 2", "Apollo", "Land", "Landing", and "Nasa". Our algorithm returns true for both Luna 2 and Apollo and return false for all others. Now, both Luna 2 and Apollo are in reality true considering the facts that Luna 2 was the first unmanned spacecraft and Apollo was the first manned spacecraft. Hence, we can't say one of the Luna 2 or Apollo as false if farther information is not given. So algorithm 2 can produce correct result for this sentence also.

\subsubsection{Sullivan is the fastest swimmer in the world}
The alternative units for this sentence are "Sullivan", "Michael phelps", "ALexander", "Long", and "Ernest". Similar to the previous sentence, the algorithm 2 can not produce good ranking for for this sentence. However, our algorithm 1 produces correct ranking and together they produce overall correct result.

\section{Rank merging}
This ranking procedure bolsters the result in the previous algorithm always without any exception. On observing the five examples above, we expect a combination of the two algorithms will give us a proper ranking of the alternate units for proper truth verification.

%\section{Conclusion}
%It this paper, we described current system for truthfulness verification of statements found in the web called T-Verifier and described the possible improvements to the current system. We will primarily use authentic information sources such as Wikipedia and Ontologies extracted from Wikipedia such as FreeBase, DBPedia, and YOGA to found the truthfulness of doubtful statements.
